Reading Notes

### 2020-08-12 2pd.tex
addressing some comments--got to the big one

In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity. %EJ: Nice- we'll mostly avoid adjectives unless they're specifically correct for something, so maybe we'd drop 'precious' here, but motivation good~
Harnessing solar energy is an important part of a green energy solution. %EJ: Why? Green energy percentage breakdown?

@@

But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative. %EJ: Cite.

@@

The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device. %EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment. %EJ: True- but we gotta make people feel this. Numbers money, time, etc
For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.

@@

By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>. %EJ: cool

@@

<what is PCE>
The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
Higher PCE means the device is more efficient.  
The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
<is there a citation for why charge transport is a good proxy for PCE?>

@@

\section*{Preliminary Work}

>>>>

In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar.\cite{https://www.eia.gov/energyexplained/renewable-sources/}
Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar. \cite{Wirth2017}

@@

But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.\cite{Tang1986b}

@@

With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Imagine, you are a chemist testing new OPVs: you are specifically looking at a mixture of a non-fullerene acceptor (ITIC) and a polymer donor (PTB7). 
Each cost \$500 for 100 mg. \cite{sigmaaldrich.com}
The solvent you use and the concentrations of your active compounds changes the device performance.\cite{Hoppe2004a}
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance. \cite{Kim2006}
The distribution of polymer lengths affects the device performance. \cite{Zhao2013b}
Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}

@@

By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>.

@@

The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device. %EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
<what is PCE>
The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
Higher PCE means the device is more efficient.  
The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
<is there a citation for why charge transport is a good proxy for PCE?>

@@

\section*{Preliminary Work}
% With lan - About excitonic splitting, using DFT, DNA. 
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
% With us - Perspective paper about all things
